---
title: "Analysis of gp41/V3 library replicates"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Purpose
I would like to determine where bottlenecks are occurring during the generation of my PhIP seq library. I have deeply sequenced 4 biological replicates of my library and will compare the correlation between read counts and coverage across the gp120 protein.

Based on prior knowledge, I am only interested in dissecting out gp120 sub lib1 and gp120 sub lib3 (these are the libraries we froze down and saved for experiments)

##Correlation between input libraries
Import relevant packages
```{r}
library(tidyverse)
library(gridExtra)
library(GGally)
```

Import annotated counts sheet (from 02/20/19)
```{r}
Input_counts <-read_csv("data/2019.02.20.annotatedCounts.csv")
print(Input_counts)
```

Get number of sequences between 10 and 100
```{r}
Input_counts %>% nrow()
Input_counts %>% subset(gp120_sub_library1 > 10) %>% subset(gp120_sub_library1 < 100) %>% nrow() 
Input_counts %>% subset(gp120_sub_library3 > 10) %>% subset(gp120_sub_library3 < 100) %>% nrow() 
```

Order from highest to lowest values in column "id"
```{r}
Input_counts <- Input_counts %>% 
  arrange(id) %>%
 print()
```

##Import the gp120 Phage-DMS library key in order to label each peptide with the correct position and WT labels
Import csv, then left join the WT table together to the analysis table

```{r}
WT_protein_tibble <- read_csv("data/gp120_PhageDMS_library_key.csv")

Input_counts <- left_join(Input_counts, WT_protein_tibble, by = c("Loc", "AA", "Virus")) 

#This is to fill in the HXB2_Loc and Correct_Loc numbers within a group
Input_counts <- Input_counts %>% 
  group_by(Virus, Loc) %>% 
  fill(HXB2_Loc, .direction = c("up")) %>%
  fill(HXB2_Loc, .direction = c("down")) %>%
  fill(Correct_Loc, .direction = c("up")) %>%
  fill(Correct_Loc, .direction = c("down")) %>%
  ungroup()
```

Graph a histogram of the read counts for each input library
```{r}
gp120_sub_library1_histogram <- count_data %>% 
  select("gp120_sub_library1") 

qplot(gp120_sub_library1_histogram$"gp120_sub_library1", geom="histogram", binwidth=5, ylab="# of peptides", xlab="read counts - Library 1") + theme_classic(base_size = 20) 
ggsave("results/library_analysis/gp120_Input_Lib1_histogram.jpg")

```

```{r}
gp120_sub_library3_histogram <- count_data %>% 
  select("gp120_sub_library3") 

qplot(gp120_sub_library3_histogram$"gp120_sub_library3", geom="histogram", binwidth=5, ylab="# of peptides", xlab="read counts - Library 2") + theme_classic(base_size = 20)

ggsave("results/library_analysis/gp120_Input_Lib2_histogram.jpg")
```

```{r}
gp120_library1_histogram <- count_data %>% 
  select("gp120_library1") 

qplot(gp120_library1_histogram$"gp120_library1", geom="histogram", binwidth=5, ylab="# of peptides", xlab="read counts - Library without subcycling") + theme_classic(base_size = 20)

ggsave("results/library_analysis/gp120_Input_Lib1_nosub_histogram.jpg")
```


Want to see how many peptides are counted 0 times in each library
```{r}
sum(gp120_sub_library1_histogram$"gp120_sub_library1" == 0)
nrow(gp120_sub_library1_histogram)
```

```{r}
sum(gp120_sub_library3_histogram$"gp120_sub_library3" == 0)
nrow(gp120_sub_library3_histogram)
```
```{r}
sum(gp120_library1_histogram$"gp120_library1" == 0)
nrow(gp120_library1_histogram)
```

Now plot correlation plots in a matrix, with regression lines
```{r}
ggpairs(Input_counts, columns=c("gp120_sub_library1", "gp120_sub_library3"), diag = list("continuous"="blank")) + theme_bw(base_size = 12)

ggsave("results/library_analysis/gp120_Input_correlations_withoutlier.jpg")
```



##Coverage of oligos across the protein, compared between libraries

Plot read count by position (aka 'Loc') for BG505_gp120 in each input library
```{r}

BG505_gp120_Lib1 <-Input_counts %>% filter(Virus == "BG505") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`gp120_sub_library1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 gp120 amino acid position", y="total reads")

BG505_gp120_Lib2 <-Input_counts %>% filter(Virus == "BG505") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`gp120_sub_library3`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 gp120 amino acid position", y="total reads")


grid.arrange(BG505_gp120_Lib1, BG505_gp120_Lib2, ncol=1)

BG505_gp120 <- arrangeGrob(BG505_gp120_Lib1, BG505_gp120_Lib2, ncol=1)

ggsave(file="results/library_analysis/gp120_coverageplots_BG505.jpg", BG505_gp120)

```

Plot read count by row number (aka 'Loc') for B41_gp120 in each input library
```{r}

B41_gp120_Lib1 <-Input_counts %>% filter(Virus == "B41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`gp120_sub_library1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="B41 gp120 amino acid position", y="total reads")

B41_gp120_Lib2 <-Input_counts %>% filter(Virus == "B41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`gp120_sub_library3`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="B41 gp120 amino acid position", y="total reads")


grid.arrange(B41_gp120_Lib1, B41_gp120_Lib2,ncol=1)

B41_gp120 <- arrangeGrob(B41_gp120_Lib1, B41_gp120_Lib2, ncol=1)

ggsave(file="results/library_analysis/gp120_coverageplots_B41.jpg", B41_gp120)

```



Plot read count by position (aka 'Loc') for DU422_gp120 in each input library
```{r}

DU422_gp120_Lib1 <-Input_counts %>% filter(Virus == "DU422")  %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`gp120_sub_library1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="DU422 gp120 amino acid position", y="total reads")

DU422_gp120_Lib2 <-Input_counts %>% filter(Virus == "DU422")  %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`gp120_sub_library3`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="DU422 gp120 amino acid position", y="total reads")

grid.arrange(DU422_gp120_Lib1, DU422_gp120_Lib2, ncol=1)

DU422_gp120 <- arrangeGrob(DU422_gp120_Lib1, DU422_gp120_Lib2, ncol=1)

ggsave(file="results/library_analysis/gp120_coverageplots_DU422.jpg", DU422_gp120)

```



Now, I am just interested in seeing if ANY peptide was sequenced at each position (yes or no). Ideally we should sequence 20 peptides at each locus at least once
Plot read presence by position (aka 'Loc') for gp120 in each gp120 protein library
```{r}
BG505_gp120_counts <- Input_counts  %>% filter(Virus=="BG505")
B41_gp120_counts <- Input_counts  %>% filter(Virus=="B41")
DU422_gp120_counts <- Input_counts  %>% filter(Virus=="DU422")


BG505_gp120_counts$peptide_yes_no_Lib1 = ifelse(BG505_gp120_counts$'gp120_sub_library1'==0,0,1)

B41_gp120_counts$peptide_yes_no_Lib1 = ifelse(B41_gp120_counts$'gp120_sub_library1'==0,0,1)

DU422_gp120_counts$peptide_yes_no_Lib1 = ifelse(DU422_gp120_counts$'gp120_sub_library1'==0,0,1)
```

##Coverage plots for gp120, Library 1
```{r}
BG505_gp120_Lib1 <- BG505_gp120_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="BG505 gp120 amino acid position", y="# of peptides") + theme_classic(base_size = 12) 

B41_gp120_Lib1 <- B41_gp120_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="B41 gp120 amino acid position", y="# of peptides") + theme_classic(base_size = 12) 

DU422_gp120_Lib1 <- DU422_gp120_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="DU422 gp120 amino acid position", y="# of peptides") + theme_classic(base_size = 12)

grid.arrange(BG505_gp120_Lib1, B41_gp120_Lib1, DU422_gp120_Lib1, ncol=1)

gp120_Lib1_coverage <- arrangeGrob(BG505_gp120_Lib1, B41_gp120_Lib1, DU422_gp120_Lib1, ncol=1)

ggsave(file="results/library_analysis/gp120_Lib1_coverageplots.jpg", gp120_Lib1_coverage, width=8)

```

```{r}
BG505_gp120_counts$peptide_yes_no_Lib2 = ifelse(BG505_gp120_counts$'gp120_sub_library3'==0,0,1)

B41_gp120_counts$peptide_yes_no_Lib2 = ifelse(B41_gp120_counts$'gp120_sub_library3'==0,0,1)

DU422_gp120_counts$peptide_yes_no_Lib2 = ifelse(DU422_gp120_counts$'gp120_sub_library3'==0,0,1)
```


```{r}
BG505_gp120_Lib2 <- BG505_gp120_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="BG505 gp120 amino acid position", y="# of peptides") + theme_classic(base_size = 12)

B41_gp120_Lib2 <- B41_gp120_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="B41 gp120 amino acid position", y="# of peptides") + theme_classic(base_size = 12) 

DU422_gp120_Lib2 <- DU422_gp120_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="DU422 gp120 amino acid position", y="# of peptides") + theme_classic(base_size = 12)

grid.arrange(BG505_gp120_Lib2, B41_gp120_Lib2, DU422_gp120_Lib2, ncol=1)

gp120_Lib2_coverage <- arrangeGrob(BG505_gp120_Lib2, B41_gp120_Lib2, DU422_gp120_Lib2, ncol=1)

ggsave(file="results/library_analysis/gp120_Lib2_coverageplots.jpg", gp120_Lib2_coverage, width=8)

```

