---
title: "Analysis of gp41/V3 library replicates"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Purpose
I would like to determine where bottlenecks are occurring during the generation of my PhIP seq library. I have deeply sequenced 4 biological replicates of my library and will compare the correlation between read counts and coverage across the gp41 protein.

##Correlation between input libraries
Import relevant packages
```{r}
library(tidyverse)
library(gridExtra)
library(GGally)
```

Import annotated counts sheet (from 10/05/18)
```{r}
Input_counts <-read_csv("data/2018.10.05.annotatedCounts.csv")
print(Input_counts)
```


Order from highest to lowest values in column "id", then select only the input columns
```{r}
Input_counts <- Input_counts %>% 
  arrange(id) %>%
  select(id, Virus_Protein_Loc_AA, "Input-Lib1", "Input-Lib2a", "Input-Lib2b", "Input-Lib2") %>%
  separate(Virus_Protein_Loc_AA, c("Virus", "Protein", "Loc", "AA"), convert = TRUE) %>%
 print()
```

##Import the gp41/V3 Phage-DMS library key in order to label each peptide with the correct position and WT labels
Import csv, then left join the WT table together to the analysis table

```{r}
WT_protein_tibble <- read_csv("data/gp41V3_PhageDMS_library_key.csv")

Input_counts <- left_join(Input_counts, WT_protein_tibble, by = c("Loc", "AA", "Virus", "Protein")) 

#This is to fill in the HXB2_Loc and Correct_Loc numbers within a group
Input_counts <- Input_counts %>% 
  group_by(Virus, Protein, Loc) %>% 
  fill(HXB2_Loc, .direction = c("up")) %>%
  fill(HXB2_Loc, .direction = c("down")) %>%
  fill(Correct_Loc, .direction = c("up")) %>%
  fill(Correct_Loc, .direction = c("down")) %>%
  ungroup()
```

Graph a histogram of the read counts for each input library
```{r}
Input_Lib1_histogram <- count_data %>% 
  select("Input-Lib1") %>% filter(`Input-Lib1` < 6000)

qplot(Input_Lib1_histogram$"Input-Lib1", geom="histogram", binwidth=5, ylab="# of peptides", xlab="read counts - Library 1") + theme_classic(base_size = 20) 
ggsave("results/library_analysis/gp41V3_Input_Lib1_histogram.jpg")

```

```{r}
Input_Lib2_histogram <- count_data %>% 
  select("Input-Lib2") %>% filter(`Input-Lib2` < 6000)

qplot(Input_Lib2_histogram$"Input-Lib2", geom="histogram", binwidth=5, ylab="# of peptides", xlab="read counts - Library 2") + theme_classic(base_size = 20)
ggsave("results/library_analysis/gp41V3_Input_Lib2_histogram.jpg")
```

Want to see how many peptides are counted 0 times in each library
```{r}
sum(Input_Lib1_histogram$"Input-Lib1" == 0)
nrow(Input_Lib1_histogram)
```

```{r}
sum(Input_Lib2_histogram$"Input-Lib2" == 0)
nrow(Input_Lib2_histogram)
```


Now plot correlation plots in a matrix, with regression lines
```{r}
ggpairs(Input_counts, columns=c("Input-Lib1", "Input-Lib2", "Input-Lib2a", "Input-Lib2b"), diag = list("continuous"="blank")) + theme_bw(base_size = 12)
ggsave("results/library_analysis/gp41V3_Input_correlations_withoutlier.jpg")
```

I would like to see the correlation without the outlier, so I am going to remove anything above 6000
```{r}
Input_counts_noOutlier <- Input_counts %>%
  filter(`Input-Lib1`< 6000) %>%
  print()
```

Now plot the correlations again, this time without the outlier
```{r}
ggpairs(Input_counts_noOutlier, columns=c("Input-Lib1", "Input-Lib2", "Input-Lib2a", "Input-Lib2b"), diag = list("continuous"="blank")) + theme_bw(base_size = 12)
ggsave("results/library_analysis/gp41V3_Input_correlations_no_outlier.jpg")
```

##Correlation between beads only controls, biological replicates
Creat new document with only beads only controls (called mock), then plot correlations, this time between beads only controls instead of input library
```{r}
Mock_counts <- count_data %>% 
  arrange(id) %>%
  select(id, Virus_Protein_Loc_AA, 'Beads-only-Lib1-1',	'Beads-only-Lib1-2',	'Beads-only-Lib2-1',	'Beads-only-Lib2-2',	'Beads-only-Lib2a',	'Beads-only-Lib2b') %>%
print()
```

Then plot correlation between biological replicates of the library
```{r}
ggpairs(Mock_counts, columns=c('Beads-only-Lib1-1',	'Beads-only-Lib2-1','Beads-only-Lib2a',	'Beads-only-Lib2b'))
ggsave("results/library_analysis/gp41V3_Mock_correlations_withoutlier.jpg")
```

Also need to get rid of the outlier, then plot the correlations again
```{r}
Mock_counts_noOutlier <- Mock_counts %>%
  filter(`Beads-only-Lib1-1`< 6000)
  
ggpairs(Mock_counts_noOutlier, columns=c('Beads-only-Lib1-1',	'Beads-only-Lib2-1','Beads-only-Lib2a',	'Beads-only-Lib2b'))
ggsave("results/library_analysis/gp41V3_Mock_correlations_no_outlier.jpg")
```

Also looking at the correlations using the second technical replicate from Lib1 and Lib2
```{r}
ggpairs(Mock_counts_noOutlier, columns=c('Beads-only-Lib1-2',	'Beads-only-Lib2-2','Beads-only-Lib2a',	'Beads-only-Lib2b'))
ggsave("results/library_analysis/gp41V3_Mock_correlationsv2_no_outlier.jpg")
```


##Correlation between beads only controls, within technical replicates
```{r}
ggpairs(Mock_counts_noOutlier, columns=c('Beads-only-Lib1-1',	'Beads-only-Lib1-2'), diag = list("continuous"="blank")) + theme_bw(base_size = 12)
ggsave("results/library_analysis/gp41V3_Mock_correlations_Lib1_technical_reps.jpg")
```

```{r}
ggpairs(Mock_counts_noOutlier, columns=c('Beads-only-Lib2-1',	'Beads-only-Lib2-2'), diag = list("continuous"="blank")) + theme_bw(base_size = 12)
ggsave("results/library_analysis/gp41V3_Mock_correlations_Lib2_technical_reps.jpg")
```

##Correlation between beads only control and input (same library)
First get rid of that pesky outlier, then plot input lib1 vs beads only with lib1
```{r}
count_data_noOutlier <- count_data %>% filter(`Beads-only-Lib1-1`< 6000)

ggpairs(count_data_noOutlier, columns=c('Input-Lib1',	'Beads-only-Lib1-1'))
ggsave("results/library_analysis/gp41V3_Lib1_mock_rep1_correlation.jpg")
```

```{r}
ggpairs(count_data_noOutlier, columns=c('Input-Lib1',	'Beads-only-Lib1-2'))
ggsave("results/library_analysis/gp41V3_Lib1_mock_rep2_correlation.jpg")
```

```{r}
ggpairs(count_data_noOutlier, columns=c('Input-Lib2',	'Beads-only-Lib2-1'))
ggsave("results/library_analysis/gp41V3_Lib2_mock_rep1_correlation.jpg")
```

```{r}
ggpairs(count_data_noOutlier, columns=c('Input-Lib2',	'Beads-only-Lib2-2'))
ggsave("results/library_analysis/gp41V3_Lib2_mock_rep2_correlation.jpg")
```


##Coverage of oligos across the protein, compared between libraries

Plot read count by position (aka 'Loc') for BG505_gp41 in each input library
```{r}

BG505_gp41_Lib1 <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 gp41 amino acid position", y="total reads")

BG505_gp41_Lib2 <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 gp41 amino acid position", y="total reads")

BG505_gp41_Lib2a <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2a`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 gp41 amino acid position", y="total reads")

BG505_gp41_Lib2b <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2b`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 gp41 amino acid position", y="total reads")


grid.arrange(BG505_gp41_Lib1, BG505_gp41_Lib2, BG505_gp41_Lib2a, BG505_gp41_Lib2b, ncol=1)

BG505_gp41 <- arrangeGrob(BG505_gp41_Lib1, BG505_gp41_Lib2, BG505_gp41_Lib2a, BG505_gp41_Lib2b, ncol=1)

ggsave(file="results/library_analysis/gp41V3_coverageplots_BG505_gp41.jpg", BG505_gp41)

```

Plot read count by row number (aka 'Loc') for BF520_gp41 in each input library
```{r}

BF520_gp41_Lib1 <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 gp41 amino acid position", y="total reads")

BF520_gp41_Lib2 <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 gp41 amino acid position", y="total reads")

BF520_gp41_Lib2a <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2a`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 gp41 amino acid position", y="total reads")

BF520_gp41_Lib2b <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2b`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 gp41 amino acid position", y="total reads")

grid.arrange(BF520_gp41_Lib1, BF520_gp41_Lib2, BF520_gp41_Lib2a, BF520_gp41_Lib2b, ncol=1)

BF520_gp41 <- arrangeGrob(BF520_gp41_Lib1, BF520_gp41_Lib2, BF520_gp41_Lib2a, BF520_gp41_Lib2b, ncol=1)

ggsave(file="results/library_analysis/gp41V3_coverageplots_BF520_gp41.jpg", BF520_gp41)

```



Plot read count by position (aka 'Loc') for ZA1197_gp41 in each input library
```{r}


ZA1197_gp41_Lib1 <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 gp41 amino acid position", y="total reads")

ZA1197_gp41_Lib2 <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 gp41 amino acid position", y="total reads")

ZA1197_gp41_Lib2a <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2a`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 gp41 amino acid position", y="total reads")

ZA1197_gp41_Lib2b <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "gp41") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2b`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 gp41 amino acid position", y="total reads")

grid.arrange(ZA1197_gp41_Lib1, ZA1197_gp41_Lib2, ZA1197_gp41_Lib2a, ZA1197_gp41_Lib2b, ncol=1)

ZA1197_gp41 <- arrangeGrob(ZA1197_gp41_Lib1, ZA1197_gp41_Lib2, ZA1197_gp41_Lib2a, ZA1197_gp41_Lib2b, ncol=1)

ggsave(file="results/library_analysis/gp41V3_coverageplots_ZA1197_gp41.jpg", ZA1197_gp41)

```



Plot read count by position (aka 'Loc') for BG505_V3 in each input library
```{r}


BG505_V3_Lib1 <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 V3 amino acid position", y="total reads")

BG505_V3_Lib2 <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 V3 amino acid position", y="total reads")

BG505_V3_Lib2a <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2a`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 V3 amino acid position", y="total reads")

BG505_V3_Lib2b <-Input_counts %>% filter(Virus == "BG505") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2b`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BG505 V3 amino acid position", y="total reads")

grid.arrange(BG505_V3_Lib1, BG505_V3_Lib2, BG505_V3_Lib2a, BG505_V3_Lib2b, ncol=1)
BG505_V3 <- arrangeGrob(BG505_V3_Lib1, BG505_V3_Lib2, BG505_V3_Lib2a, BG505_V3_Lib2b, ncol=1)
ggsave(file="results/library_analysis/gp41V3_coverageplots_BG505_V3.jpg", BG505_V3, width=8)

```




Plot read count by position (aka 'id') for BF520_V3 in each input library
```{r}

BF520_V3_Lib1 <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 V3 amino acid position", y="total reads") 

BF520_V3_Lib2 <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 V3 amino acid position", y="total reads") 

BF520_V3_Lib2a <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2a`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 V3 amino acid position", y="total reads") 

BF520_V3_Lib2b <-Input_counts %>% filter(Virus == "BF520") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2b`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="BF520 V3 amino acid position", y="total reads")  

grid.arrange(BF520_V3_Lib1, BF520_V3_Lib2, BF520_V3_Lib2a, BF520_V3_Lib2b, ncol=1)

BF520_V3 <- arrangeGrob(BF520_V3_Lib1, BF520_V3_Lib2, BF520_V3_Lib2a, BF520_V3_Lib2b, ncol=1)

ggsave(file="results/library_analysis/gp41V3_coverageplots_BF520_V3.jpg", BF520_V3)

```


Plot read count by position (aka 'id') for ZA1197_V3 in each input library
```{r}

ZA1197_V3_Lib1 <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib1`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 V3 amino acid position", y="total reads") 

ZA1197_V3_Lib2 <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 V3 amino acid position", y="total reads") 

ZA1197_V3_Lib2a <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2a`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 V3 amino acid position", y="total reads") 

ZA1197_V3_Lib2b <-Input_counts %>% filter(Virus == "ZA1197") %>% filter(Protein == "V3") %>% group_by(Correct_Loc) %>% summarise(read_total = sum(`Input-Lib2b`)) %>% ggplot() + geom_col(aes(x = Correct_Loc, y =read_total)) + theme_classic() +labs(x="ZA1197 V3 amino acid position", y="total reads")    

grid.arrange(ZA1197_V3_Lib1, ZA1197_V3_Lib2, ZA1197_V3_Lib2a, ZA1197_V3_Lib2b, ncol=1)

ZA1197_V3 <- arrangeGrob(ZA1197_V3_Lib1, ZA1197_V3_Lib2, ZA1197_V3_Lib2a, ZA1197_V3_Lib2b, ncol=1)

ggsave(file="results/library_analysis/gp41V3_coverageplots_ZA1197_V3.jpg", ZA1197_V3)

```

Now, I am just interested in seeing if ANY peptide was sequenced at each position (yes or no). Ideally we should sequence 20 peptides at each locus at least once
Plot read presence by position (aka 'Loc') for gp41 in each gp41 protein library
```{r}
BG505_gp41_counts <- Input_counts %>% filter(Protein=="gp41") %>% filter(Virus=="BG505")
BF520_gp41_counts <- Input_counts %>% filter(Protein=="gp41") %>% filter(Virus=="BF520")
ZA1197_gp41_counts <- Input_counts %>% filter(Protein=="gp41") %>% filter(Virus=="ZA1197")


BG505_gp41_counts$peptide_yes_no_Lib1 = ifelse(BG505_gp41_counts$'Input-Lib1'==0,0,1)
BF520_gp41_counts$peptide_yes_no_Lib1 = ifelse(BF520_gp41_counts$'Input-Lib1'==0,0,1)
ZA1197_gp41_counts$peptide_yes_no_Lib1 = ifelse(ZA1197_gp41_counts$'Input-Lib1'==0,0,1)
```

##Coverage plots for gp41, Library 1
```{r}
BG505_gp41_Lib1 <- BG505_gp41_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="BG505 gp41 amino acid position", y="# of peptides") + theme_classic(base_size = 12) 

BF520_gp41_Lib1 <- BF520_gp41_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="BF520 gp41 amino acid position", y="# of peptides") + theme_classic(base_size = 12) 

ZA1197_gp41_Lib1 <- ZA1197_gp41_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="ZA1197 gp41 amino acid position", y="# of peptides") + theme_classic(base_size = 12)

grid.arrange(BG505_gp41_Lib1, BF520_gp41_Lib1, ZA1197_gp41_Lib1, ncol=1)

gp41_Lib1_coverage <- arrangeGrob(BG505_gp41_Lib1, BF520_gp41_Lib1, ZA1197_gp41_Lib1, ncol=1)

ggsave(file="results/library_analysis/gp41V3_Lib1_coverageplots_gp41.jpg", gp41_Lib1_coverage)

```

```{r}
BG505_gp41_counts$peptide_yes_no_Lib2 = ifelse(BG505_gp41_counts$'Input-Lib2'==0,0,1)
BF520_gp41_counts$peptide_yes_no_Lib2 = ifelse(BF520_gp41_counts$'Input-Lib2'==0,0,1)
ZA1197_gp41_counts$peptide_yes_no_Lib2 = ifelse(ZA1197_gp41_counts$'Input-Lib2'==0,0,1)
```


```{r}
BG505_gp41_Lib2 <- BG505_gp41_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="BG505 gp41 amino acid position", y="# of peptides") + theme_classic(base_size = 12)

BF520_gp41_Lib2 <- BF520_gp41_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="BF520 gp41 amino acid position", y="# of peptides") + theme_classic(base_size = 12) 

ZA1197_gp41_Lib2 <- ZA1197_gp41_counts %>% ggplot() + geom_col(aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="ZA1197 gp41 amino acid position", y="# of peptides") + theme_classic(base_size = 12)

grid.arrange(BG505_gp41_Lib2, BF520_gp41_Lib2, ZA1197_gp41_Lib2, ncol=1)

gp41_Lib2_coverage <- arrangeGrob(BG505_gp41_Lib2, BF520_gp41_Lib2, ZA1197_gp41_Lib2, ncol=1)

ggsave(file="results/library_analysis/gp41V3_Lib2_coverageplots_gp41.jpg", gp41_Lib2_coverage)

```

Now, I am just interested in seeing if ANY peptide was sequenced at each position (yes or no). Ideally we should sequence 20 peptides at each locus at least once
Plot read presence by position (aka 'Loc') for V3 in each gp41 protein library
```{r}
BG505_V3_counts <- Input_counts %>% filter(Protein=="V3") %>% filter(Virus=="BG505")
BF520_V3_counts <- Input_counts %>% filter(Protein=="V3") %>% filter(Virus=="BF520")
ZA1197_V3_counts <- Input_counts %>% filter(Protein=="V3") %>% filter(Virus=="ZA1197")

BG505_V3_counts$peptide_yes_no_Lib1 = ifelse(BG505_V3_counts$'Input-Lib1'==0,0,1)
BF520_V3_counts$peptide_yes_no_Lib1 = ifelse(BF520_V3_counts$'Input-Lib1'==0,0,1)
ZA1197_V3_counts$peptide_yes_no_Lib1 = ifelse(ZA1197_V3_counts$'Input-Lib1'==0,0,1)
```

```{r}
BG505_V3_Lib1 <- ggplot() + geom_col(data = BG505_V3_counts, aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="BG505 V3 amino acid position", y="# of peptides") + theme_classic() +coord_fixed(ratio=1)

BF520_V3_Lib1 <- ggplot() + geom_col(data = BF520_V3_counts, aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="BF520 V3 amino acid position", y="# of peptides") + theme_classic() +coord_fixed(ratio=1)

ZA1197_V3_Lib1 <- ggplot() + geom_col(data = ZA1197_V3_counts, aes(x = Correct_Loc, y =peptide_yes_no_Lib1), width=1) + labs(x="ZA1197 V3 amino acid position", y="# of peptides") + theme_classic() +coord_fixed(ratio=1)

grid.arrange(BG505_V3_Lib1, BF520_V3_Lib1, ZA1197_V3_Lib1, ncol=1)

V3_Lib1_coverage <- arrangeGrob(BG505_V3_Lib1, BF520_V3_Lib1, ZA1197_V3_Lib1, ncol=1)

ggsave(file="results/library_analysis/gp41V3_Lib1_coverageplots_V3.jpg", V3_Lib1_coverage)

```

```{r}
BG505_V3_counts$peptide_yes_no_Lib2 = ifelse(BG505_V3_counts$'Input-Lib2'==0,0,1)
BF520_V3_counts$peptide_yes_no_Lib2 = ifelse(BF520_V3_counts$'Input-Lib2'==0,0,1)
ZA1197_V3_counts$peptide_yes_no_Lib2 = ifelse(ZA1197_V3_counts$'Input-Lib2'==0,0,1)
```

```{r}
BG505_V3_Lib2 <- ggplot() + geom_col(data = BG505_V3_counts, aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="BG505 V3 amino acid position", y="# of peptides") + theme_classic() +coord_fixed(ratio=1)

BF520_V3_Lib2 <- ggplot() + geom_col(data = BF520_V3_counts, aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="BF520 V3 amino acid position", y="# of peptides") + theme_classic() +coord_fixed(ratio=1)

ZA1197_V3_Lib2 <- ggplot() + geom_col(data = ZA1197_V3_counts, aes(x = Correct_Loc, y =peptide_yes_no_Lib2), width=1) + labs(x="ZA1197 V3 amino acid position", y="# of peptides") + theme_classic() +coord_fixed(ratio=1)

grid.arrange(BG505_V3_Lib2, BF520_V3_Lib2, ZA1197_V3_Lib2, ncol=1)

V3_Lib2_coverage <- arrangeGrob(BG505_V3_Lib2, BF520_V3_Lib2, ZA1197_V3_Lib2, ncol=1)

ggsave(file="results/library_analysis/gp41V3_Lib2_coverageplots_V3.jpg", V3_Lib2_coverage)


```