---
title: "Analysis of 447-52D selection with gp41/V3 Phage-DMS libraries"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Code to analyze the deep sequencing results from a PhIP seq experiment
Generally I get back sequencing data back from Ryan Basom in an "annotated counts sheet" with read counts from each sample/bead/input condition. Here is a list of all the columns of data I get back in the annotated counts sheet: 
* id: this is a unique number identifying each oligo
* Virus_Protein_Loc_AA: This is a column with each identifier separated by an underscore. 
  + Virus is the viral strain we generated oligos against (ex: BG505, BF520, etc)
  + Protein is the Env protein (ex: gp120, gp41, V3)
  + Loc is the locus within the protein, starting from the first amino acid of the protein
  + AA is the amino acid identity of the central residue in the oligo sequence (which has every single amino acid possibility)
* Oligo: This column contains the nucleotide sequence of the unique oligo, with the 18 bp 5' adaptor and 16 bp 3' adaptor
* samples: can be read counts from antibody selected, bead selected, or input library conditions. Here is the universal naming scheme:
  + Antibody selected samples will have an x before the name (ex: x44752D) as several antibodies have numbered names (which R doesn't like) 
  + Technical replicates will have an _1 or _2 after the name (ex: beads_1, input_1)
  + The beads-only selected condition will be named "beads"
  + The input library condition will be named "input"

##Load libraries
```{r}
library(tidyverse)
library(GGally)
library(gridExtra)
library(ggpubr)
library(reshape2)
```

**FIRST REPLICATE**
##Load data, separate out columns, generate column with oligo sequence without the adaptors
Load annotated counts sheet
```{r}
analysis_rep1 <-read_csv("data/2019.02.04.annotatedCounts.csv")

print(analysis_rep1)
```

Now I need to split up the column name "Virus_Protein_Loc_AA" 
```{r}
analysis_rep1 <- analysis_rep1 %>% 
  separate(Virus_Protein_Loc_AA, c("Virus", "Protein", "Loc", "AA"), convert = TRUE)
```

Create column called "sequence" which has the nucleotide sequence of the peptides displayed on the surface of the phage. Adaptors are 18 bp (5') and 16 bp (3').
```{r}
analysis_rep1$sequence = substr(analysis_rep1$Oligo,19,nchar(analysis_rep1$Oligo)-16)

print(analysis_rep1)
```

##Import the gp41/V3 Phage-DMS library key in order to label each peptide with the correct position and WT labels
Import csv, then left join the WT table together to the analysis table

```{r}
WT_protein_tibble <- read_csv("data/gp41V3_PhageDMS_library_key.csv")

analysis_rep1 <- left_join(analysis_rep1, WT_protein_tibble, by = c("Loc", "AA", "Virus", "Protein")) 

#This is to fill in the HXB2_Loc and Correct_Loc numbers within a group
analysis_rep1 <- analysis_rep1 %>% 
  group_by(Virus, Protein, Loc) %>% 
  fill(HXB2_Loc, .direction = c("up")) %>%
  fill(HXB2_Loc, .direction = c("down")) %>%
  fill(Correct_Loc, .direction = c("up")) %>%
  fill(Correct_Loc, .direction = c("down")) %>%
  ungroup()
```


##Examine correlation between technical replicates
Only continue analyzing samples which have higher than 75% reproducibility (except for beads, which doesn't usually have very high reproducibility since there's more chance involved)

Right now I am manually doing this for all samples tested, but would love to do this in a loop!
```{r}
correlation_tibble <- data.frame(sample = 'x44752D', correlation = cor(analysis_rep1$x44752D_1,analysis_rep1$x44752D_2),stringsAsFactors = F) %>% as_tibble  

correlation_tibble <- add_row(correlation_tibble, sample = 'beads', correlation = cor(analysis_rep1$beads_1,analysis_rep1$beads_2)) 

print(correlation_tibble)

```

Just for shits and giggles, I'm going to remove the outlier and then redo the correlations

```{r}
analysis_rep1_no_outlier <- analysis_rep1 %>% select(x44752D_1, x44752D_2, beads_1, beads_2, input_1) %>%  filter_all(all_vars(.< 6000))

```

```{r}
correlation_tibble_no_outlier <- data.frame(sample = 'x44752D', correlation = cor(analysis_rep1_no_outlier$x44752D_1,analysis_rep1_no_outlier$x44752D_2),stringsAsFactors = F) %>% as_tibble  

correlation_tibble_no_outlier <- add_row(correlation_tibble_no_outlier, sample = 'beads', correlation = cor(analysis_rep1_no_outlier$beads_1,analysis_rep1_no_outlier$beads_2)) 


print(correlation_tibble_no_outlier)

```


Now plot the correlations (without the outlier). Right now I am doing this with a simple scatter plot, but in the future I should maybe consider doing a ggpairs correlation plot.
```{r}
x44752D_correlation <- ggplot(analysis_rep1_no_outlier, aes(x=x44752D_1, y=x44752D_2)) + geom_point()
ggsave(file = "results/mAb_analysis/gp41V3_44752D/x44752D_correlation_rep1.jpg", x44752D_correlation)

beads_correlation <- ggplot(analysis_rep1_no_outlier, aes(x=beads_1, y=beads_2)) + geom_point()
ggsave(file = "results/mAb_analysis/gp41V3_44752D/beads_correlation_rep1.jpg", beads_correlation)


```

```{r}
x2019_02_04_correlation_plots <- grid.arrange(arrangeGrob(x44752D_correlation, beads_correlation, ncol=2, top="2019.02.04 correlation plots"))


ggsave(file="results/mAb_analysis/gp41V3_44752D/2019_02_04_correlation_plots.jpg", x2019_02_04_correlation_plots)
```

```{r}
x44752D_correlation <- ggplot(analysis_rep1_no_outlier, aes(x=x44752D_1, y=x44752D_2)) + geom_point() +stat_cor(method="pearson", size = 8) + xlab("read counts - technical replicate 1") +ylab("read counts - technical replicate 2") + theme_classic(base_size = 24)


ggsave(file = "results/mAb_analysis/gp41V3_44752D/x44752D_correlation_rep1_fig.jpg", x44752D_correlation)
```

##Add together technical replicates
Add together the read counts from the two technical replicates of the beads only, input, and antibody selections. 
```{r}
analysis_rep1$sum_44752D <- analysis_rep1$`x44752D_1` + analysis_rep1$`x44752D_2`

analysis_rep1$sum_input <- analysis_rep1$`input_1` 
```



##Calculate the fold enrichment of WT peptides across each Virus/Protein combination
Right now I am just looking at the fold enrichment of single peptides centered at a residue, but alternatively I could calculate fold enrichment by finding the average enrichment of any peptide spanning a residue (+/- 15 aa, since the peptides are 31 aa long). Fold enrichment is calculated as freq_sample / freq_input. 


Calculate the freq of each peptide in each of the samples. Freq = read count/total read count. 

Need to add a pseudocount to each peptide's read count. I scale this according to the read depth (see explanation from the Bloom lab [here](https://jbloomlab.github.io/dms_tools2/diffsel.html#formula-for-differential-selection))
Calculate pseudocount for each column with a sample (ex: input, beads, and 44752D sample). Treat the beads condition as a sample (aka compare against every antibody/beads sample against the input).

Because the pseudocount is added as a relative weight, we can only add a pseudocount to the input library when we know which sample we are comparing against. Since this code is only analyzing antibody 44752D, I'm adding the pseudocount now. Non-input samples will always be compared to the input to generate a pseudocount.

```{r}
analysis_rep1 <- analysis_rep1 %>% mutate(sum_44752D_pseudo = case_when( 
  sum(sum_44752D) / sum(sum_input) < 1 ~ sum_44752D + 1, 
  sum(sum_44752D) / sum(sum_input) >= 1 ~ sum_44752D +(sum(sum_44752D) / sum(sum_input))*1))

analysis_rep1 <- analysis_rep1 %>% mutate(sum_input_pseudo = case_when( 
  sum(sum_input) / sum(sum_44752D) < 1 ~ sum_input + 1, 
  sum(sum_input) / sum(sum_44752D) >= 1 ~ sum_input +(sum(sum_input) / sum(sum_44752D))*1))


```



Now calculate the frequency of each peptide in the samples
```{r}
analysis_rep1 <- analysis_rep1 %>% 
  mutate(freq_44752D = sum_44752D_pseudo / sum(sum_44752D_pseudo)) %>% 
  mutate(freq_input = sum_input_pseudo/sum(sum_input_pseudo))

```

Now calculate the site-level fold enrichment of all wildtype peptides in the 44752D sample, as compared to the input


Right now this only calculates the fold enrichment of WT peptides - I'd like to instead calculat the fold enrichment of all peptides, and later filter by WT when exporting to test with FindSigSel function.
```{r}
analysis_rep1 <- analysis_rep1 %>% mutate(fold_enrich_44752D = freq_44752D/freq_input) %>% print()

```

Now plot the fold enrichment across the length of each protein
**BG505 gp41**
```{r}
fold_enrichment_44752D_BG505_gp41 <- analysis_rep1 %>% filter(Protein == 'gp41' & Virus == 'BG505' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BG505 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BG505_gp41_rep1.jpg", fold_enrichment_44752D_BG505_gp41, width=8)
```

**BF520 gp41**
```{r}
fold_enrichment_44752D_BF520_gp41 <- analysis_rep1 %>% filter(Protein == 'gp41' & Virus == 'BF520' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BF520 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BF520_gp41_rep1.jpg", fold_enrichment_44752D_BF520_gp41, width=8)
```

**ZA1197 gp41**
```{r}
fold_enrichment_44752D_ZA1197_gp41 <- analysis_rep1 %>% filter(Protein == 'gp41' & Virus == 'ZA1197' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "ZA1197 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_ZA1197_gp41_rep1.jpg", fold_enrichment_44752D_ZA1197_gp41, width=8)
```

**BG505 V3**
```{r}
fold_enrichment_44752D_BG505_V3 <- analysis_rep1 %>% filter(Protein == 'V3' & Virus == 'BG505' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BG505 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BG505_V3_rep1.jpg", fold_enrichment_44752D_BG505_V3, width=8)
```

**BF520 V3**
```{r}
fold_enrichment_44752D_BF520_V3 <- analysis_rep1 %>% filter(Protein == 'V3' & Virus == 'BF520' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BF520 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BF520_V3_rep1.jpg", fold_enrichment_44752D_BF520_V3, width=8)
```

**ZA1197 V3**
```{r}
fold_enrichment_44752D_ZA1197_V3 <- analysis_rep1 %>% filter(Protein == 'V3' & Virus == 'ZA1197' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "ZA1197 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_ZA1197_V3_rep1.jpg", fold_enrichment_44752D_ZA1197_V3, width=8)
```



##Differential selection calculations
Create a column that calculates the mutation-level differential selection. NOTE: I'm not adjusting for mock selected (beads only) condition


Create columns with WT frequencies from the 44752D and input conditions.
```{r}
WT_freq_44752D <- analysis_rep1 %>% 
  filter(type == "WT") %>% 
  select(Loc,Virus, Protein, freq_44752D_WT=freq_44752D) 

analysis_rep1 <- left_join(analysis_rep1, WT_freq_44752D)

WT_freq_input <- analysis_rep1 %>% 
  filter(type == "WT") %>% 
  select(Loc, Virus, Protein, freq_input_WT=freq_input) 

analysis_rep1 <- left_join(analysis_rep1, WT_freq_input)

```

Now calculate the differential selection
```{r}
analysis_rep1 <- analysis_rep1 %>% mutate(diff_select_44752D = log((freq_44752D/freq_44752D_WT)/(freq_input/freq_input_WT)))
```


##Now calculate the scaled differential selection: multiply the mutation level differential selection and the site level fold enrichment and plot it

Now create a column with the fold enrichment value of the WT , so that I can calculate the scaled differential selection. There has to be a better way to insert the fold enrichment value of the WT peptide, but I can't figure it out. 

If I was subtracting the beads fold enrichment from the sample's fold enrichment, I would need to first take the absolute value of the fold enrichment (this is a hacky way to deal with the negative numbers). But I am not subtracting out the beads, so I don't need to do that!
```{r}
fold_enrich_44752D <- analysis_rep1 %>% 
  select(Loc, Virus, Protein, fold_enrich_44752D_WT=fold_enrich_44752D, type) %>% 
  filter(type == "WT") %>% 
  select(Loc, Virus, Protein, fold_enrich_44752D_WT) 

analysis_rep1 <- left_join(analysis_rep1, fold_enrich_44752D)
```

Now multiply the fold enrichment by the differential selection to get the scaled differential selection.
```{r}
analysis_rep1 <- analysis_rep1 %>% mutate(scaled_diff_select_44752D = (diff_select_44752D)*(fold_enrich_44752D_WT))
```


Now plot the scaled differential selection for each Virus/protein combo for the sample 
***BG505_V3***
```{r}
letter_plot_44752D_BG505_V3 <- analysis_rep1 %>% filter(Virus == 'BG505' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = scaled_diff_select_44752D, label = AA)) +coord_fixed(ratio=0.5) +theme_classic(base_size = 14) +labs(x="BG505 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_BG505_V3_rep1.jpg", letter_plot_44752D_BG505_V3, width=10)
```


***BF520_V3***
```{r}
letter_plot_44752D_BF520_V3 <- analysis_rep1 %>% filter(Virus == 'BF520' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = scaled_diff_select_44752D, label = AA)) +coord_fixed(ratio=2) +theme_classic(base_size = 14) +labs(x="BF520 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_BF520_V3_rep1.jpg", letter_plot_44752D_BF520_V3, width=10)
```


***ZA1197_V3***
```{r}
letter_plot_44752D_ZA1197_V3 <- analysis_rep1 %>% filter(Virus == 'ZA1197' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = scaled_diff_select_44752D, label = AA)) +coord_fixed(ratio=1) +theme_classic(base_size = 14) +labs(x="ZA1197 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_ZA1197_V3_rep1.jpg", letter_plot_44752D_ZA1197_V3, width=10)
```





**SECOND REPLICATE**
##NOW, I will do all of the above for the 2nd replicate, and then in the end average them
##Load data, separate out columns, generate column with oligo sequence without the adaptors
Load annotated counts sheet
```{r}
analysis_rep2 <-read_csv("data/2019.04.02.Lib1.annotatedCounts.csv")

print(analysis_rep2)
```

Now I need to split up the column name "Virus_Protein_Loc_AA" 
```{r}
analysis_rep2 <- analysis_rep2 %>% 
  separate(Virus_Protein_Loc_AA, c("Virus", "Protein", "Loc", "AA"), convert = TRUE)
```

Create column called "sequence" which has the nucleotide sequence of the peptides displayed on the surface of the phage. Adaptors are 18 bp (5') and 16 bp (3').
```{r}
analysis_rep2$sequence = substr(analysis_rep2$Oligo,19,nchar(analysis_rep2$Oligo)-16)

print(analysis_rep2)
```

##Import the gp41/V3 Phage-DMS library key in order to label each peptide with the correct position and WT labels
Import csv, then left join the WT table together to the analysis table

```{r}
WT_protein_tibble <- read_csv("data/gp41V3_PhageDMS_library_key.csv")

analysis_rep2 <- left_join(analysis_rep2, WT_protein_tibble, by = c("Loc", "AA", "Virus", "Protein")) 

#This is to fill in the HXB2_Loc and Correct_Loc numbers within a group
analysis_rep2 <- analysis_rep2 %>% 
  group_by(Virus, Protein, Loc) %>% 
  fill(HXB2_Loc, .direction = c("up")) %>%
  fill(HXB2_Loc, .direction = c("down")) %>%
  fill(Correct_Loc, .direction = c("up")) %>%
  fill(Correct_Loc, .direction = c("down")) %>%
  ungroup()
```

##Examine correlation between technical replicates
Only continue analyzing samples which have higher than 75% reproducibility (except for beads, which doesn't usually have very high reproducibility since there's more chance involved)

Right now I am manually doing this for all samples tested, but would love to do this in a loop!
```{r}
correlation_tibble <- data.frame(sample = 'x44752D', correlation = cor(analysis_rep2$x44752D_1,analysis_rep2$x44752D_2),stringsAsFactors = F) %>% as_tibble  

correlation_tibble <- add_row(correlation_tibble, sample = 'beads', correlation = cor(analysis_rep2$beads_1,analysis_rep2$beads_2)) 

correlation_tibble <- add_row(correlation_tibble, sample = 'input', correlation = cor(analysis_rep2$input_1,analysis_rep2$input_2)) 

print(correlation_tibble)

```

Just for shits and giggles, I'm going to remove the outlier and then redo the correlations

```{r}
analysis_rep2_no_outlier <- analysis_rep2 %>% select(x44752D_1, x44752D_2, beads_1, beads_2, input_1, input_2) %>%  filter_all(all_vars(.< 5500))

```

```{r}
correlation_tibble_no_outlier <- data.frame(sample = 'x44752D', correlation = cor(analysis_rep2_no_outlier$x44752D_1,analysis_rep2_no_outlier$x44752D_2),stringsAsFactors = F) %>% as_tibble  

correlation_tibble_no_outlier <- add_row(correlation_tibble_no_outlier, sample = 'beads', correlation = cor(analysis_rep2_no_outlier$beads_1,analysis_rep2_no_outlier$beads_2)) 

correlation_tibble_no_outlier <- add_row(correlation_tibble_no_outlier, sample = 'input', correlation = cor(analysis_rep2_no_outlier$input_1,analysis_rep2_no_outlier$input_2)) 

print(correlation_tibble_no_outlier)

```


Now plot the correlations (without the outlier). Right now I am doing this with a simple scatter plot, but in the future I should maybe consider doing a ggpairs correlation plot.
```{r}
x44752D_correlation <- ggplot(analysis_rep2_no_outlier, aes(x=x44752D_1, y=x44752D_2)) + geom_point()
ggsave(file = "results/mAb_analysis/gp41V3_44752D/x44752D_correlation_rep2.jpg", x44752D_correlation)

beads_correlation <- ggplot(analysis_rep2_no_outlier, aes(x=beads_1, y=beads_2)) + geom_point()
ggsave(file = "results/mAb_analysis/gp41V3_44752D/beads_correlation_rep2.jpg", beads_correlation)

input_correlation <- ggplot(analysis_rep2_no_outlier, aes(x=input_1, y=input_2)) + geom_point()
ggsave(file = "results/mAb_analysis/gp41V3_44752D/input_correlation_rep2.jpg", input_correlation)


```

```{r}
x2019_02_04_Lib1_correlation_plots <- grid.arrange(arrangeGrob(x44752D_correlation, beads_correlation, input_correlation, ncol=2, top="2019.02.04 Lib1 correlation plots"))


ggsave(file="results/mAb_analysis/gp41V3_44752D/2019_02_04_Lib1_correlation_plots.jpg", x2019_02_04_Lib1_correlation_plots)
```

```{r}
x44752D_correlation <- ggplot(analysis_rep2_no_outlier, aes(x=x44752D_1, y=x44752D_2)) + geom_point() +stat_cor(method="pearson", size = 8) + xlab("read counts - technical replicate 1") +ylab("read counts - technical replicate 2") + theme_classic(base_size = 24)


ggsave(file = "results/mAb_analysis/gp41V3_44752D/x44752D_correlation_rep2_fig.jpg", x44752D_correlation)
```

##Add together technical replicates
Add together the read counts from the two technical replicates of the beads only, input, and antibody selections. 
```{r}
analysis_rep2$sum_44752D <- analysis_rep2$`x44752D_1` + analysis_rep2$`x44752D_2`

analysis_rep2$sum_input <- analysis_rep2$`input_1` + analysis_rep2$`input_2` 
```



##Calculate the fold enrichment of WT peptides across each Virus/Protein combination
Right now I am just looking at the fold enrichment of single peptides centered at a residue, but alternatively I could calculate fold enrichment by finding the average enrichment of any peptide spanning a residue (+/- 15 aa, since the peptides are 31 aa long). Fold enrichment is calculated as freq_sample / freq_input. 


Calculate the freq of each peptide in each of the samples. Freq = read count/total read count. 

Need to add a pseudocount to each peptide's read count. I scale this according to the read depth (see explanation from the Bloom lab [here](https://jbloomlab.github.io/dms_tools2/diffsel.html#formula-for-differential-selection))
Calculate pseudocount for each column with a sample (ex: input, beads, and 44752D sample). Treat the beads condition as a sample (aka compare against every antibody/beads sample against the input).

Because the pseudocount is added as a relative weight, we can only add a pseudocount to the input library when we know which sample we are comparing against. Since this code is only analyzing antibody 44752D, I'm adding the pseudocount now. Non-input samples will always be compared to the input to generate a pseudocount.

```{r}
analysis_rep2 <- analysis_rep2 %>% mutate(sum_44752D_pseudo = case_when( 
  sum(sum_44752D) / sum(sum_input) < 1 ~ sum_44752D + 1, 
  sum(sum_44752D) / sum(sum_input) >= 1 ~ sum_44752D +(sum(sum_44752D) / sum(sum_input))*1))

analysis_rep2 <- analysis_rep2 %>% mutate(sum_input_pseudo = case_when( 
  sum(sum_input) / sum(sum_44752D) < 1 ~ sum_input + 1, 
  sum(sum_input) / sum(sum_44752D) >= 1 ~ sum_input +(sum(sum_input) / sum(sum_44752D))*1))

```

Now calculate the frequency of each peptide in the samples
```{r}
analysis_rep2 <- analysis_rep2 %>% 
  mutate(freq_44752D = sum_44752D_pseudo / sum(sum_44752D_pseudo)) %>% 
  mutate(freq_input = sum_input_pseudo/sum(sum_input_pseudo))

```

Now calculate the site-level fold enrichment of all wildtype peptides in the 44752D sample, as compared to the input


Right now this only calculates the fold enrichment of WT peptides - I'd like to instead calculate the fold enrichment of all peptides, and later filter by WT when exporting to test with FindSigSel function.
```{r}
analysis_rep2 <- analysis_rep2 %>% mutate(fold_enrich_44752D = freq_44752D/freq_input) %>% print()
```

Now plot the fold enrichment across the length of each protein
**BG505 gp41**
```{r}
fold_enrichment_44752D_BG505_gp41 <- analysis_rep2 %>% filter(Protein == 'gp41' & Virus == 'BG505' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BG505 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BG505_gp41_rep2.jpg", fold_enrichment_44752D_BG505_gp41, width=8)
```

**BF520 gp41**
```{r}
fold_enrichment_44752D_BF520_gp41 <- analysis_rep2 %>% filter(Protein == 'gp41' & Virus == 'BF520' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BF520 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BF520_gp41_rep2.jpg", fold_enrichment_44752D_BF520_gp41, width=8)
```

**ZA1197 gp41**
```{r}
fold_enrichment_44752D_ZA1197_gp41 <- analysis_rep2 %>% filter(Protein == 'gp41' & Virus == 'ZA1197' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "ZA1197 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_ZA1197_gp41_rep2.jpg", fold_enrichment_44752D_ZA1197_gp41, width=8)
```

**BG505 V3**
```{r}
fold_enrichment_44752D_BG505_V3 <- analysis_rep2 %>% filter(Protein == 'V3' & Virus == 'BG505' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BG505 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BG505_V3_rep2.jpg", fold_enrichment_44752D_BG505_V3, width=8)
```

**BF520 V3**
```{r}
fold_enrichment_44752D_BF520_V3 <- analysis_rep2 %>% filter(Protein == 'V3' & Virus == 'BF520' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BF520 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_BF520_V3_rep2.jpg", fold_enrichment_44752D_BF520_V3, width=8)
```

**ZA1197 V3**
```{r}
fold_enrichment_44752D_ZA1197_V3 <- analysis_rep2 %>% filter(Protein == 'V3' & Virus == 'ZA1197' & type == 'WT') %>% ggline( x='Loc', y = 'fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "ZA1197 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/fold_enrichment_44752D_ZA1197_V3_rep2.jpg", fold_enrichment_44752D_ZA1197_V3, width=8)
```


##Differential selection calculations
Create a column that calculates the mutation-level differential selection. NOTE: I'm not adjusting for mock selected (beads only) condition


Create columns with WT frequencies from the 44752D and input conditions.
```{r}
WT_freq_44752D <- analysis_rep2 %>% 
  filter(type == "WT") %>% 
  select(Loc,Virus, Protein, freq_44752D_WT=freq_44752D) 

analysis_rep2 <- left_join(analysis_rep2, WT_freq_44752D)

WT_freq_input <- analysis_rep2 %>% 
  filter(type == "WT") %>% 
  select(Loc, Virus, Protein, freq_input_WT=freq_input) 

analysis_rep2 <- left_join(analysis_rep2, WT_freq_input)

```

Now calculate the differential selection
```{r}
analysis_rep2 <- analysis_rep2 %>% mutate(diff_select_44752D = log((freq_44752D/freq_44752D_WT)/(freq_input/freq_input_WT)))
```

##Now calculate the scaled differential selection: multiply the mutation level differential selection and the site level fold enrichment and plot it

Now create a column with the fold enrichment value of the WT , so that I can calculate the scaled differential selection. There has to be a better way to insert the fold enrichment value of the WT peptide, but I can't figure it out. 

If I was subtracting the beads fold enrichment from the sample's fold enrichment, I would need to first take the absolute value of the fold enrichment (this is a hacky way to deal with the negative numbers). But I am not subtracting out the beads, so I don't need to do that!

```{r}
fold_enrich_44752D <- analysis_rep2 %>% 
  select(Loc, Virus, Protein, fold_enrich_44752D_WT=fold_enrich_44752D, type) %>% 
  filter(type == "WT") %>% 
  select(Loc, Virus, Protein, fold_enrich_44752D_WT) 

analysis_rep2 <- left_join(analysis_rep2, fold_enrich_44752D)
```

Now multiply the fold enrichment by the differential selection to get the scaled differential selection.
```{r}
analysis_rep2 <- analysis_rep2 %>% mutate(scaled_diff_select_44752D = (diff_select_44752D)*(fold_enrich_44752D_WT))
```



Now plot the scaled differential selection for each Virus/protein combo for the sample 
***BG505_V3***
```{r}
letter_plot_44752D_BG505_V3 <- analysis_rep2 %>% filter(Virus == 'BG505' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = scaled_diff_select_44752D, label = AA)) +coord_fixed(ratio=1) +theme_classic(base_size = 14) +labs(x="BG505 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_BG505_V3_rep2.jpg", letter_plot_44752D_BG505_V3, width=10)
```


***BF520_V3***
```{r}
letter_plot_44752D_BF520_V3 <- analysis_rep2 %>% filter(Virus == 'BF520' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = scaled_diff_select_44752D, label = AA)) +coord_fixed(ratio=2) +theme_classic(base_size = 14) +labs(x="BF520 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_BF520_V3_rep2.jpg", letter_plot_44752D_BF520_V3, width=10)
```

***ZA1197_V3***

```{r}
letter_plot_44752D_ZA1197_V3 <- analysis_rep2 %>% filter(Virus == 'ZA1197' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = scaled_diff_select_44752D, label = AA)) +coord_fixed(ratio=1) +theme_classic(base_size = 14) +labs(x="ZA1197 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_ZA1197_V3_rep2.jpg", letter_plot_44752D_ZA1197_V3, width=10)
```



##Average the biological duplicates!!
Need to average the fold enrichment values and the differential selection values, then re plot the fold enrichment along the proteins, and the scaled differential selection

Create new table, with the fold enrichment values and differential selection values from each replicate
```{r}
avg_analysis <- analysis_rep1 %>% select(id, Virus, Protein, Loc, AA, type, HXB2_Loc, Correct_Loc, rep1_sum_44752D=sum_44752D, rep1_fold_enrich_44752D=fold_enrich_44752D, rep1_scaled_diff_select_44752D=scaled_diff_select_44752D)
```

```{r}
rep2 <- analysis_rep2 %>% select(id, Virus, Protein, Loc, AA, type, HXB2_Loc, Correct_Loc, rep2_sum_44752D=sum_44752D, rep2_fold_enrich_44752D=fold_enrich_44752D, rep2_scaled_diff_select_44752D=scaled_diff_select_44752D) 

avg_analysis <- left_join(rep2, avg_analysis)

```
##Now plot the correlation between biological duplicates
```{r}
x44752D_correlation <- ggplot(avg_analysis, aes(x=rep1_sum_44752D, y=rep2_sum_44752D)) + geom_point()+stat_cor(method="pearson", size = 8) + xlab("read counts - biological replicate 1") +ylab("read counts - biological replicate 2") + theme_classic(base_size = 24)

ggsave(file = "results/mAb_analysis/gp41V3_44752D/x44752D_correlation_biological_duplicates.jpg", x44752D_correlation)
```
Now remove the outlier, and then redo the biological duplicates
```{r}
avg_analysis_no_outlier <- avg_analysis %>% select(rep1_sum_44752D, rep2_sum_44752D) %>% filter_all(all_vars(.< 20000))


x44752D_correlation <- ggplot(avg_analysis_no_outlier, aes(x=rep1_sum_44752D, y=rep2_sum_44752D)) + geom_point()
ggsave(file = "results/mAb_analysis/gp41V3_44752D/x44752D_correlation_biological_duplicates_nooutlier.jpg", x44752D_correlation)
```


```{r}
correlation_tibble_no_outlier <- data.frame(sample = 'x44752D', correlation = cor(avg_analysis_no_outlier$rep1_sum_44752D,avg_analysis_no_outlier$rep2_sum_44752D),stringsAsFactors = F) %>% as_tibble

print(correlation_tibble_no_outlier)
```

##Now average the fold enrichment values
```{r}
avg_analysis <- avg_analysis %>% mutate(avg_fold_enrich_44752D = (rep1_fold_enrich_44752D + rep2_fold_enrich_44752D)/2)
```


Now plot the fold enrichment across the length of each protein
**BG505 gp41**
```{r}
fold_enrichment_44752D_BG505_gp41 <- avg_analysis %>% filter(Protein == 'gp41' & Virus == 'BG505' & type == 'WT') %>% ggline( x='Loc', y = 'avg_fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BG505 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrich_44752D_BG505_gp41_rep2.jpg", fold_enrichment_44752D_BG505_gp41, width=8)
```

**BF520 gp41**
```{r}
fold_enrichment_44752D_BF520_gp41 <- avg_analysis %>% filter(Protein == 'gp41' & Virus == 'BF520' & type == 'WT') %>% ggline( x='Loc', y = 'avg_fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BF520 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrich_44752D_BF520_gp41_rep2.jpg", fold_enrichment_44752D_BF520_gp41, width=8)
```

**ZA1197 gp41**
```{r}
fold_enrichment_44752D_ZA1197_gp41 <- avg_analysis %>% filter(Protein == 'gp41' & Virus == 'ZA1197' & type == 'WT') %>% ggline( x='Loc', y = 'avg_fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "ZA1197 gp41 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrich_44752D_ZA1197_gp41_rep2.jpg", fold_enrichment_44752D_ZA1197_gp41, width=8)
```

**Combined V3**
```{r}
library(ggpubr)
fold_enrichment_44752D_V3 <- avg_analysis %>% filter(Protein == 'V3' & type == 'WT') %>% ggline( x='HXB2_Loc', y = 'avg_fold_enrich_44752D', group = 'Virus', color = 'Virus', palette = 'Dark2', add = NULL, conf.int = FALSE, cor.coef = FALSE, xlab = "HXB2 Env amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 22) + scale_x_discrete( breaks = c(290, 300, 310, 320))

fold_enrichment_44752D_V3 <- ggpar(fold_enrichment_44752D_V3, ylim = c(-1, 20), legend=c(.9,.8))

ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrichment_44752D_V3.jpg", fold_enrichment_44752D_V3, width=10)
```

**BG505 V3**
```{r}
fold_enrichment_44752D_BG505_V3 <- avg_analysis %>% filter(Protein == 'V3' & Virus == 'BG505' & type == 'WT') %>% ggline( x='Loc', y = 'avg_fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BG505 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrich_44752D_BG505_V3_rep2.jpg", fold_enrichment_44752D_BG505_V3, width=8)
```

**BF520 V3**
```{r}
fold_enrichment_44752D_BF520_V3 <- avg_analysis %>% filter(Protein == 'V3' & Virus == 'BF520' & type == 'WT') %>% ggline( x='Loc', y = 'avg_fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "BF520 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrich_44752D_BF520_V3_rep2.jpg", fold_enrichment_44752D_BF520_V3, width=8)
```

**ZA1197 V3**
```{r}
fold_enrichment_44752D_ZA1197_V3 <- avg_analysis %>% filter(Protein == 'V3' & Virus == 'ZA1197' & type == 'WT') %>% ggline( x='Loc', y = 'avg_fold_enrich_44752D',
                   add = NULL, conf.int = FALSE,
                   cor.coef = FALSE,
                   xlab = "ZA1197 V3 amino acid position", ylab = "fold enrichment") +theme_classic(base_size = 14) 
ggsave(file="results/mAb_analysis/gp41V3_44752D/avg_fold_enrich_44752D_ZA1197_V3_rep2.jpg", fold_enrichment_44752D_ZA1197_V3, width=8)
```


##Now average together the scaled differential selection values
```{r}
avg_analysis <- avg_analysis %>% mutate(avg_scaled_diffselect_44752D = (rep1_scaled_diff_select_44752D + rep2_scaled_diff_select_44752D)/2)
```

Now plot the scaled differential selection for each Virus/protein combo for the sample 
***BG505_V3***
```{r}
letter_plot_44752D_BG505_V3 <- avg_analysis %>% filter(Virus == 'BG505' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = avg_scaled_diffselect_44752D, label = AA)) +coord_fixed(ratio=0.4) +theme_classic(base_size = 14) +labs(x="BG505 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_BG505_V3_avg.jpg", letter_plot_44752D_BG505_V3, width = 8, height = 6)
```


***BF520_V3***
```{r}
letter_plot_44752D_BF520_V3 <- avg_analysis %>% filter(Virus == 'BF520' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = avg_scaled_diffselect_44752D, label = AA)) +coord_fixed(ratio=2) +theme_classic(base_size = 14) +labs(x="BF520 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_BF520_V3_avg.jpg", letter_plot_44752D_BF520_V3, width=10)
```

***ZA1197_V3***

```{r}
letter_plot_44752D_ZA1197_V3 <- avg_analysis %>% filter(Virus == 'ZA1197' & Protein == 'V3') %>%
  ggplot() + geom_text(aes(x = Loc, y = avg_scaled_diffselect_44752D, label = AA)) +coord_fixed(ratio=1) +theme_classic(base_size = 14) +labs(x="ZA1197 V3 amino acid position", y="scaled differential selection") 
ggsave(file="results/mAb_analysis/gp41V3_44752D/letter_plot_44752D_ZA1197_V3_avg.jpg", letter_plot_44752D_ZA1197_V3, width=10)
```

##Now, I want to export the scaled diff selection data to visualize as a heatmap
I will have to export it as a table just looking within the epitope region, need to reorder it as a matrix and one column has to have the position and WT aa (ex: G559)

First I need to create a new row that has the position and WT aa
```{r}
#First create a new column 
avg_analysis_extra <- avg_analysis %>%
  filter(type == "WT") %>%
  unite(Title, c(AA, HXB2_Loc), sep = "", remove = FALSE) %>%
  select(Title, Virus, Protein, Loc)

avg_analysis <- left_join(avg_analysis, avg_analysis_extra, by = c("Virus", "Protein", "Loc"))

```


Now, create a matrix just with the BG505 gp41 data
```{r}
#This pulls the scaled differential selection data from just BG505 gp41, only want region of epitope. Right now this is arbitrary.

BG505_V3_matrix <- avg_analysis %>% 
  filter(Virus == 'BG505' & Protein == 'V3') %>% 
  select(Title, AA, avg_scaled_diffselect_44752D) %>%
  acast(AA ~ Title)
```

Now reorder the columns to match the order they were in before (this is because R automatically orders the columns alphabetically, which is not what I want)
```{r}
#Create a data frame with just the WT Titles from the epitope region
BG505_V3_df <- avg_analysis %>% 
  filter(Virus == 'BG505' & Protein == 'V3' & type == 'WT') 
  
#This stores the values in the column "Title" as a vector
col.order <- as.vector(BG505_V3_df$Title)

#This rearranges the matrix so that the order is the same as in the vector created above
BG505_V3_matrix <- BG505_V3_matrix[,col.order]
```

Now reorder the rows to match the order they were in before (this is because R automatically orders the rows alphabetically, which is not what I want)
```{r}
#This stores the order of the specified amino acids as a vector
row.order <- c("G", "P", "A", "I", "L", "V", "F", "W", "Y", "M", "C", "S", "T", "N", "Q", "H", "K", "R", "D", "E")

#This rearranges the rows according to the row order vector
BG505_V3_matrix <- BG505_V3_matrix[row.order,]
```


Now export this matrix as a table
```{r}
write.csv(BG505_V3_matrix, file="results/mAb_analysis/gp41V3_44752D/BG505_V3_44752D_matrix.csv")
```

